Reproducibility in Plant Pathology

### 2021-09-29 README.rmd
Update README files
Add tic badge and edit text

# Reproducibility in Plant Pathology
![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

This repository contains the data and code for our paper:

>>>>

# Reproducibility in Plant Pathology
<!-- badges: start -->
![Publish Docker](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/Publish%20Docker/badge.svg)
[![tic](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/workflows/tic/badge.svg?branch=main)](https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/actions)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges: end -->

This repository contains the data and code for our letter to the editor:
